\chapter{Overview of radical inventions}\label{chap:inventions}

\section{Introduction}
In this chapter, we perform the assessment of five inventions based on the
framework described in \autoref{chap:intro}. Chapter \ref{chap:imaging}
already described various breakthroughs in diagnostic medical imaging, but most of them
predate 1980. Fortunately researchers in the field have come up with plenty of
other innovations in the last thirty years, some of which will be detailed
below. We included one invention per imaging modality described, plus one more
related to computer aided detection and diagnosis (CAD).

For each innovation, a technological definition is provided wherein the purpose
or goal is outlined, and the components plus their interactions are explained
based on a thorough literature review. Next, the innovation is scored based on
the assessment sheet in \autoref{app:score}.

\input{sections/31_radio.tex}

\input{sections/32_ct.tex}

\input{sections/33_mri.tex}

\input{sections/34_pet.tex}

\input{sections/35_cad.tex}

\section{Conclusion}
In this chapter, we presented the results of the assessment of various
innovations related to diagnostic medical imaging. We tried to be as varied as
possible in the selection of innovations. Not only did they all stem from a
different field, but their scope and type also varied. For example, we tried a
high-level assessment of MRI as a whole, but also assessment of a whole class of
algorithms and a very specific radiopharmaceutical compound. In our newfound
experience, the assessment framework seems to work best on rather low-level, yet
tangible innovations. Nonetheless, it showed considerable flexibility when
applied to concepts it was perhaps never intended for.

Truthfully, we are slightly disappointed by the seemingly low scores of these
important innovations. We explore some reasons for this in the following
paragraphs.

We have tried to make this assessment as detailed as possible. However, medical
imaging is a very complex matter, and even our introduction in
\autoref{chap:imaging} - much like many a review paper - just barely scratch the
surface of all underlying methods and technologies. These details only become
apparent when hands-on work is performed by scientists and researchers in the
field. For example, a little known fact is that the anode in an X-ray tube gets
hot during operation, lowering performance. A simple solution is to make it spin
to cool it down. Such details will only be described in the most detailed
literature and of course in patent applications. We fear that this discrepancy
in level of detail will significantly hamper comparison with the automated
patent analysis.

The way the framework is built also seems to favor automatic patent based
analysis over manual assessment. The questions on the assessment sheet map
nicely to data that can be extracted from patents. On the other hand, manually
finding an answer to these questions without looking at patent data has proven
to be challenging at times. The granularity of the scores presents another
problem. It is very difficult to explain the difference between, for example, a
5 and a 6. In that regard we would either propose a rescaled score chart with
scores from 1 to 5. The alternative is to improve the existing score chart with a more
detailed description of how to quantify the small differences in score.

In addition, the 1980 limit made it significantly more difficult to go back to
the real breakthrough invention, the so-called seed. For example, FDG in nuclear
medicine was certainly a breakthrough but it would have been more interesting to
go back further and see who first managed to bring nuclear physics together with
biochemistry and truly invent radiopharmacology. The fact that many
imaging-related inventions spend a very long time in the research phase, taking
decades before entering the market, does not help in this regard either. On the
other hand, due to the ex-post nature of some assessment questions (i.e.,
impact), very recent innovations cannot be mapped either.

One final aspect we noticed, is that medical imaging research seems to ``stay in
the family'' - so to speak. One imaging modality builds on top of another
modality's knowledge, but the technology hardly seems to diffuse into other
fields. One possible explanation is that biomedical researchers have plenty of
very specific medicine-related journals to choose from for publishing, so they
don't branch out. They do not interact much with journals that have similar
content, but focus on another sector. From personal experience, this is very
apparent in the image processing literature. For example, one can browse image
processing journals from IEEE in vain without finding a solution for a generic
non-medical problem. Meanwhile, medical researchers might have come up with such
a solution years ago, applied it to medicine and published it in a medical image
processing journal.