%\chapter*{Abstract\hfill}\addcontentsline{toc}{chapter}{Abstract}

\cleardoublepage
\thispagestyle{plain}
\begin{center}
    \Huge 
    Identification of important contributions in diagnostic medical imaging
    
    \vspace{0.5cm}
    
    \large
    Identificatie van belangrijke contributies in diagnostische medische beeldvorming
    
    \vspace{1.0cm}
    
    Sven Van Hove, Dennis Verhoeven, Reinhilde Veugelers
    
    \vspace{0.5cm}
    
	Managerial Economics, Strategy and Innovation (MSI)\\
	Faculteit Economie en Bedrijfswetenschappen\\
	KU Leuven
    
    \vspace{1.0cm}
    \textbf{Abstract}
\end{center}

Radical innovations have the power to disrupt whole technological fields, and
are often seen as a key factor in long term growth. Therefore it is critical to
identify early on how radical an innovation is. In this thesis, we performed a
manual assessment of five interesting innovations in the field of diagnostic medical
imaging: digital radiography, electron beam computed tomography, magnetic
resonance imaging, 18F-FDG tracers in nuclear medicine and the application of
computer aided detection and diagnosis in mammography. The assessment was
performed based on a framework proposed by \cite{verhoeven}. This framework
contains three dimensions: novelty of knowledge origins, novelty of
functionality  and technological impact. The resulting scores turned out lower
than expected, so we looked into possible causes. In the future these scores can
be compared against the outcome of an automatic assessment based on patent
indicators. Conclusions drawn from this comparison could be used to optimize the
framework.

\vspace{1.0cm}

\textbf{Keywords:} important technological inventions, radical innovation,
diagnostic medical imaging, manual assessment, patent indicators.