\chapter{Introduction to diagnostic medical imaging}\label{chap:imaging}

\section{Introduction}
In this chapter, we provide an overview of diagnostic medical imaging and its
history. Medical imaging is a field in medicine concerned with creating visual
representations of a body for the purpose of clinical analysis. Although medical
imaging is sometimes used for non-diagnostic purposes, we will only concern
ourselves with diagnostic medical imaging. This subbranch has the goal to
facilitate diagnosis of medical conditions without the need for invasive
procedures. Over the past fifty years, this discipline has matured
significantly, it has become indispensable in the modern age medical setting
\cite{review}.

The most important aspect of diagnostic medical imaging is image production, but
various other aspects are involved. Image processing, image display, image
recording, image transmission and image storage are all related. Modern day
Picture Archiving and Communication Systems (PACS) provide all these features.
Once the image has been captured and processed, it can be presented to a
radiologist for diagnosis. In recent years, scientists have focused on
augmenting the physician's diagnostic ability with various Computer Aided
Diagnosis (CAD) schemes. For example, algorithms based on machine learning are
able to autonomously detect lung nodules with ever increasing accuracy
\cite{ginneken}. Although some systems aim to make physicians redundant in the
long term, most experts agree that software should augment them rather than
replace them entirely \cite{cadhistory}.

In the next sections, we will discuss the history, technical background and
recent advancements of the most important imaging modalities.

\input{sections/21_radio.tex}

\input{sections/22_ct.tex}

\input{sections/23_mri.tex}

\input{sections/24_pet.tex}

\input{sections/25_img.tex}